%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\usepackage{fontawesome}



\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Rahul}{Parmar}{ % Your name

\href{mailto:rahulparmar.n@gmail.com}{rahulparmar.n@gmail.com} | +91 8200771907 % Your contact information
| Github:// \href{https://github.com/RahulParmarRP}{\bf RahulParmarRP} |
LinkedIn:// \href{https://www.linkedin.com/in/rahul-parmar-rp/}{\bf rahul-parmar-rp} \\  % Your website, LinkedIn profile or other web address

}


%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page






%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\textbf{Over 5000 lines:}
\begin{itemize}
\setlength\itemsep{-0.5em} % Adjust the vertical space between items
\item JavaScript (ES6)
\item TypeScript
\end{itemize}

\textbf{Over 1000 lines:}
\begin{itemize}
\setlength\itemsep{-0.5em} % Adjust the vertical space between items
\item NodeJS
\item C\#
\end{itemize}

\textbf{Frameworks / Libraries:}
\begin{itemize}
\setlength\itemsep{-0.5em} % Adjust the vertical space between items
\item React
\item Redux
\item Next.js
\end{itemize}


\textbf{Other tools/technologies/languages:}
\begin{itemize}
\setlength\itemsep{-0.5em} % Adjust the vertical space between items
\item HTML
\item CSS
\item Responsive Design
\item Git
\item Micro-Frontend (MFE)
\item Web Accessibility (WCAG)
\item Unit Testing
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{B. H. Gardi College Of Engineering and Technology}

\descript{(B.E.) Bachelor of Engineering in Computer Engineering}
\location{Graduated: Jun 2019 | Rajkot, Gujarat}
\textbf{CGPA:} 8.0 / 10.0

\sectionspace % Some whitespace after the section

\subsection{Shree P. V. Modi School}

\descript{Higher Secondary Education}
\location{Graduated: May 2013 | Rajkot, Gujarat}
\textbf{Percentage:} 82.6%

\sectionspace % Some whitespace after the section

\subsection{Saint Gargy High School}

\descript{Secondary Education}
\location{Graduated: Jun 2015 | Rajkot, Gujarat}
\textbf{Percentage:} 89.5%

\sectionspace % Some whitespace after the section




%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

Python 101 \\
Web Accessibility \\
NodeJS \\
\sectionspace % Some whitespace after the section


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page


%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}

\runsubsection{Publicis Sapient}
\descript{| Software Engineer L2}

\location{Feb 2022 – Present | Bengaluru (Remote) }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Working with Next.js, React.js, HTML, Sass, CSS, and A11y to develop micro front-end apps and maintain a component library.
\item Actively engaged in client communication, daily stand-up meetings, and sprint grooming/planning sessions, ensuring alignment with Agile principles and timely delivery of project milestones.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{TatvaSoft}
\descript{| Software Engineer}

\location{Jun 2019 – Feb 2022 | Ahmedabad}
\begin{tightitemize}
\item Contributed as a front-end developer specializing in React.js, and Next.js involved in team management and client communication.
\item Started as an Associate Software Engineer, focusing on React.js development.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{TatvaSoft}
\descript{| Intern}

\location{Jan 2019 – Apr 2019 | Ahmedabad}
\begin{tightitemize}
\item Engaged in project development and received training in various aspects of software engineering.
\end{tightitemize}

\sectionspace % Some whitespace after the section






%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects}

\subsection{US Bank | Branch Locator\href{https://www.usbank.com/locations/search/}{\faExternalLink} and Advisor Locator\href{https://www.usbank.com/wealth-management/find-an-advisor/}{\faExternalLink}}

\textbf{React | NextJS | Typescript | Microfrontend | Module Federation}  \\
Contributed as a Front-End dev for the transformation of a traditional enterprise app by using Microfrontend and ISR within Next.js for real-time data updates in both the Branch Locator and Advisor Locator apps.

\textbf{Resulting in a remarkable 50\% reduction in website loading time, enhanced SEO, and improved accessibility.}

Streamlined development efforts through \textbf{Micro-Frontend Architecture and Shared Component library, resulting in cost-effective solutions}.

showcased our excellence by
streamlining \textbf{the search for 4000+ bank branches and
ATMs and over 2000 financial advisors}, while maintaining performance efficiency.

Additionally, users can visit individual pages of branches or advisors, enhancing the overall user journey.

The integration of Google Maps enhanced user
experience and features like Nearby Location Search
and Advanced Result Filtering added significant value.


\sectionspace % Some whitespace after the section

\subsection{TRENDii - AI-based Fashion Discovery, Shoppable Ads, }


\textbf{React.js | JavaScript | Redux | Next.js | Typescript | Material UI | Chrome Extension} \\
Led front-end architecture and system design for an innovative AI-powered Fashion Discovery platform, TRENDii.

Conducted extensive research and development to enhance platform features and functionalities.

Developed and maintained JavaScript libraries, including the cutting-edge TRENDii Shoppable Ads SDK.

Developed Chrome browser extensions and integrated social media logins and integrated payment gateways including Google Pay, PayPal, and Stripe.

Boosted productivity as a Full Stack Developer by creating a single-page application for generating complex financial documentation, achieving 3X efficiency gains for a Canadian banking client.

\sectionspace % Some whitespace after the section

\runsubsection{SchoolArt | HTML Canvas based Educational Web App}
\descript{| Head Undergrad Research}

\location{Jan 2014 – Present | Ithaca, NY}
Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which learns from large scale user preference feedback to plan robot trajectories in human environments. Publication submitted.

\sectionspace % Some whitespace after the section


\subsection{SchoolArt | HTML Canvas based Educational Web App}


\textbf{React.js | Fabric.js | HTML Canvas | RazorPay integration} \\

Contributed to system architecture and various feature developments, including tools for drawing, modifying canvas designs, and managing canvas objects.
Conducted extensive research and development to enhance platform features and functionalities.
Integrated social media logins (Google and Facebook) for user authentication and seamless user experience.

Boosted productivity as a Full Stack Developer by creating a single-page application for generating complex financial documentation, achieving 3X efficiency gains for a Canadian banking client.

\sectionspace % Some whitespace after the section



%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
